Revealing Benefits, Costs, and Tradeoffs of Spatial Management in Marine Systems Arrising from Coupled Economic and Ecological Dynamics

### 2023-04-03 03_marlin_paper.qmd
added option for coastal MPA design ands fixed some equation alignments

$$
n_{t,p,s,a = 1} = \left(\frac{0.8{\times}\sum_{p=1}^P{r0_{p,s}}\times{h_s}\times\sum_{p=1}^P{ssb_{t-1,p,s}}}{0.2\times{\sum_{p=1}^Pssb0_{p,s}}\times(1 - h_s)+(h_s - 0.2)\times{\sum_{p=1}^Pssb_{t-1,p,s}}}\right)\times {r0_{p,s} / \sum_p^P{r0_{p,s}}\times \epsilon_{t,s}
}
$$ {#eq-dd2}

@@

$$
n_{t,p,s,a = 1} = \left(\frac{0.8{\times}\sum_{p=1}^P{r0_{p,s}}\times{h_s}\times\sum_{p=1}^P{ssb_{t-1,p,s}}}{0.2\times{\sum_{p=1}^Pssb0_{p,s}}\times(1 - h_s)+(h_s - 0.2)\times{\sum_{p=1}^Pssb_{t-1,p,s}}}\right)\times \frac{ssb_{t-1,p,s}}{\sum_{p=1}^Pssb_{t-1,p,s}} \times \epsilon_{t,s}
$$ {#eq-dd5}

>>>>

$$
\begin{aligned}
n_{t,p,s,a = 1} = \left(\frac{0.8{\times}\sum_{p=1}^P{r0_{p,s}}\times{h_s}\times\sum_{p=1}^P{ssb_{t-1,p,s}}}{0.2\times{\sum_{p=1}^Pssb0_{p,s}} \times(1 - h_s)+(h_s - 0.2) \times{\sum_{p=1}^Pssb_{t-1,p,s}}}\right) \times \\ {r0_{p,s} / \sum_p^P{r0_{p,s}}\times \epsilon_{t,s}
}
\end{aligned}
$$ {#eq-dd2}

@@

$$
\begin{aligned}
n_{t,p,s,a = 1} = \left(\frac{0.8{\times}\sum_{p=1}^P{r0_{p,s}}\times{h_s}\times\sum_{p=1}^P{ssb_{t-1,p,s}}}{0.2\times{\sum_{p=1}^Pssb0_{p,s}}\times(1 - h_s)+(h_s - 0.2)\times{\sum_{p=1}^Pssb_{t-1,p,s}}}\right) \times \\ \frac{ssb_{t-1,p,s}}{\sum_{p=1}^Pssb_{t-1,p,s}} \times \epsilon_{t,s}
\end{aligned}
$$ {#eq-dd5}
